%% cheat sheet
% Dokumentformatierung
	% \\				< Zeilenumbruch
	% \par				< Absatz mit Einrückung
	% \\[0.5cm]			< Absatz mit Abstand
	% \newpage			< Neue Seite
	% \part 			< Teil
	% \chapter 			< Kapitel
	% \section 			< Unterüberschrift
	% \subsection 		< Unterunterüberschrift

% Textformatierung
	% \glqq{}foo\{}		< Anführungszeichen
	% \textit{foo}		< Kursiv
	% \textbf{foo}		< Fett
	% \underline{foo}	< Unterstrichsen

% ----------------------------------------------------------------------
% Dokumentenklasse / Definitionen
\documentclass[a4paper,11pt]{scrartcl}% Format des Dokuments
\usepackage[utf8]{inputenc}% Interpreter
\usepackage[ngerman] {babel}% Definition des Sprachraums
\usepackage[T1] {fontenc}% Schriftart
\usepackage {graphicx}% Erlaubt das einfügen von Bildern

% Kopf- Fußzeile
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{LF 8 / Hiss}
\chead{Thema: Der Ausbildungsvertrag}
\rhead{Datum: 10.11.2014}
\lfoot{\thepage}
\cfoot{}
\rfoot{Lars Hendrik Friedrichsen - Version 1.0 - \today}


% Header
\title{today\author{Lars Friedrichsen}}

\begin{document}

\section{Time-Table}

\begin{tabular}{|l|l|}
	\hline
	Time		&	tour item\\ \hline
	9:30-10:00	&	Company's history and organisation\ldots\\ \hline
	10:00-12:00	&	marketing, order processing, customer service\\ \hline
	12:00-13:00	&	lunch break\\ \hline
	13:00-15:00	&	R\&D\\ \hline
	15:00-		&	final meeting in the conference room Q\&A\\ \hline
\end{tabular}

\section{From the customer's point of view, does it matter where the call centre is?}
	
	\subsection{The language matters}
	The idea of outsourcing a call centre could come to a rather quick end, if the language isn't a part of calculation.
	The customer calling is likely to have an issue of some kind, meaning that he isn't in the best mood. This is a 
	very important fact to consider, because the communication over the phone isn't like talking to someone face to face.\par
	Now imagine this customer getting pushed through into a line where a person is answering, who is not utilize the
	language completely. This can be taken as given due to the fact that a native speaker would be abble to dominate the
	agent. This leads to a point where the call agent isn't able to offer a proper solution to a person who already is
	angry. You can imagine that this customer is likely to escalate which puts the call agent in a even worse position.
	So the customer doesn't get a satisfying sollution to his problem and the company would get a bad review.\par
	These things lead to the conclusion that the language is the most important thing in this case. So from a customer's
	standpoint it would be unacceptable.

	\subsection{People have different value systems}
	Talking about value systems is pretty hard and a personal matter. No person is the same, which leads to the point
	that everyone has a different value system. From experience I can tell that customers like to ask where the call 
	agent is located.\par
	Now, what does it have to do with a person's value system? This can be explained in an easy way. There are people who
	like to support the local economy instead of paying some random person from some place he didn't even hear about.
	This is also directly relatet to a company's reputation because the call agent is the first and most often the conly
	direct contact a customer has with a company.

	\subsection{Don't forget about culture}
	People are different in many ways and this also relates to the different value systems they have. Culture is also 
	a huge topic when talking about communication. The same expression in one culture might mean a total different thing
	in the other. This can be a really strong point which can lead to misunderstandings. To drive this point home:\par
	There are different cultures even in one country. Now imagine the huge diversity multinationaly. A customer might
	offends the call agent with a normal expression and wonders why the service person doesn't want to help.

	\subsection{Conclusion}
	In a nutshell: Due to the points mentioned above the call centre's location can matter a lot especially when it comes
	to misunderstandings. The company wants to hold customers and the customers want the service. In order to satisfy
	both needs the location is a big issue and shouldn't be underestimated.

\end{document}
	
