%% cheat sheet
% Dokumentformatierung
	% \\				< Zeilenumbruch
	% \par				< Absatz mit Einrückung
	% \\[0.5cm]			< Absatz mit Abstand
	% \newpage			< Neue Seite
	% \part 			< Teil
	% \chapter 			< Kapitel
	% \section 			< Unterüberschrift
	% \subsection 		< Unterunterüberschrift

% Textformatierung
	% \glqq{}foo\{}		< Anführungszeichen
	% \textit{foo}		< Kursiv
	% \textbf{foo}		< Fett
	% \underline{foo}	< Unterstrichsen

% ----------------------------------------------------------------------

% Dokumentenklasse / Definitionen
\documentclass[a4paper,11pt]{scrartcl}	% Format des Dokuments
\usepackage[utf8]{inputenc}				% Interpreter
\usepackage[ngerman] {babel}			% Definition des Sprachraums
\usepackage[T1] {fontenc}				% Schriftart
\usepackage {graphicx}					% Erlaubt das einfügen von Bildern

% Kopf- Fußzeile
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{English / Nissen}
\chead{Topic: present tense}
\rhead{Date: 05.11.2014}
\lfoot{\thepage}
\cfoot{}
\rfoot{Lars Hendrik Friedrichsen - Version 1.0 - \today}


% Header
\title{Thema}			
\author{Lars Friedrichsen}
\date{\today}

% Dokument / Printing 
\begin{document}

\section{IT International - FAQ}

	\begin{enumerate}
		\item \textbf{What is IT International?}\par
		It is a multinational telecomunications and information technology company.		
		\item \textbf{Where is IT International located?}\par
		The headquarters is in Munich.
		\item \textbf{Where are the company's subsidiaries?}\par
		They have subsidiaries in 30 countries (Asia, Africa, the US and Europe).
		\item \textbf{What is special about China?}\par
		China is the fastest growing market.
		\item \textbf{How many people work for IT International?}\par
		IT International has 180,650 employees.
		\item \textbf{What are the company's business activities?}\par
		They supply network access, communication services, fixed and mobile networks and telephnes / cell phones.
		\item \textbf{What is IT International's business philosophy?}\par
		Their philosophy is to provide their customers with excellent products and services at fair prices.
	\end{enumerate}

\section{vocabulary}

\begin{tabular}{|l|l|}
	\hline
	headquarters		&		a place from which something is controlled \\ \hline
	revenue				&		the total annual income of a company\\ \hline
	subsidiary			&		a company that is owned by a larger company\\ \hline
	employee			&		a person who works for a company\\ \hline
	access				&		a way into something\\ \hline
	focus on			&		to concentrate on\\ \hline
	determine			&		to decide something firmly\\ \hline
	provide				&		to offer\\ \hline
\end{tabular}

\newpage

\section{Practice - present tenses}

\begin{enumerate}
	\item At the moment our company is growing quickly.
	\item That is why we are needing to recruit new staff right now.
	\item We have subsidiaries in many countries.
	\item Peter works in technical support.
	\item He helps when customers are having problems.
	\item Just now we are developing new software.
	\item We usually give our customers good value for money.
	\item Today we are offering a discount of 10 per cent.
\end{enumerate}

\section{Filling in the gaps}

\begin{enumerate}
	\item How can I \textbf{help} you?
	\item I have an \textbf{appointment} with Ms Wang but I'm \textbf{afraid} I'm a few minutes early.
	\item \textbf{Welcome} to Munich Mr. Matthesws.
	\item I'll \textbf{let} Maggie \textbf{know} that you're here.
	\item If you could just \textbf{wait} a moment, I'm \textbf{sure} she'll be here soon.
	\item I don't \textbf{mind} waiting.
	\item Pleased to \textbf{meet} you.
	\item I hope you \textbf{enjoy} your stay in Munich.
\end{enumerate}

\end{document}
	