%% cheat sheet
% Dokumentformatierung
	% \\				< Zeilenumbruch
	% \par				< Absatz mit Einrückung
	% \\[0.5cm]			< Absatz mit Abstand
	% \newpage			< Neue Seite
	% \part 			< Teil
	% \chapter 			< Kapitel
	% \section 			< Unterüberschrift
	% \subsection 		< Unterunterüberschrift

% Textformatierung
	% \glqq{}foo\{}		< Anführungszeichen
	% \textit{foo}		< Kursiv
	% \textbf{foo}		< Fett
	% \underline{foo}	< Unterstrichsen

% ----------------------------------------------------------------------
% Dokumentenklasse / Definitionen
\documentclass[a4paper,11pt]{scrartcl}% Format des Dokuments
\usepackage[utf8]{inputenc}% Interpreter
\usepackage[ngerman] {babel}% Definition des Sprachraums
\usepackage[T1] {fontenc}% Schriftart
\usepackage {graphicx}% Erlaubt das einfügen von Bildern

% Kopf- Fußzeile
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{LF  / Nissen }
\chead{Thema: Telephone conversation}
\rhead{Datum: 19.11.2014}
\rfoot{\thepage}
\cfoot{}
\lfoot{Lars Hendrik Friedrichsen - Version 1.0 - \today}


% Header
\title{today\author{Lars Friedrichsen}}

\begin{document}

\section{Telephone phrases}

	\subsection{Listening}

	\begin{enumerate}
		\item What is the customer's question?\par
			Customer can't import spreadsheets into the document.
		
		\item What help does the operator give?\par
			The operator wants to call back, because the needed line was busiy.
	\end{enumerate}

	\subsection{Telephone conversation}

		\begin{itemize}
			\item Superword helpline, this is Lars speaking. How can I help you?
			\item The line seems to be bad. Could you speak up a little?
			\item Sorry to hear that. I'm afraid, that I'm not able to help you here.
				May I put you through to the PDF department?
			\item Then please hold the line for a moment.
			\item I'm sorry but the number is busy.
			\item So, could I ask my colleges to get back to you?
			\item Thanks for calling in. Have a nice day.
		\end{itemize}

	\subsection{Changing questions}
		\begin{enumerate}
			\item What time does the flight leave?\par
				Could you tell at what time the flight leaves?
			\item Which terminal does it leave from?\par
				May I ask at which terminal it leaves from?
			\item How far is the factory from the airport?\par
				Could you tell me how far the factory is from the airport?
			\item Which car hiring company is it?\par
				Can you tell me which car hiring carompany it is?
			\item Which models do they have available?\par
				an you tell me what models are available?
			\item Do I need an international driving licence?\par
				Could you tell me wheter I need an international driving licence?
			\item Where are we staying?\par
				Could you tell me where we are going to stay?
			\item Is it a nice place?\par
				Do you know wether it is a nice place?
			\item Have they booked a meeting room?\par
				Do you know if they had booked a meeting room?
		\end{enumerate}

	\subsection{YAE - Yet Another Exercise}
	
		\begin{enumerate}
			\item Look! Tim \underline{is wearing} a tie. Usually he only \underline{wears} T-shirts.
			\item Trevor \underline{plays} football every Saturday.
			\item You can't talk to dad now. He is \underline{watching} a football match on TV.
			\item Ann \underline{is workin} in the garden. She \underline{is playnting} some flowers. She
				always \underline{plants} all the flowers herself.
			\item Listen!. My neighbour \underline{is playing} his stupid Elvis Presley record again.
				He \underline{plays} the same record every evening.
			\item The River Thames \underline{flows} into the North Sea.
			\item Graham \underline{speaks} five foreign languages.
			\item This teacher never \underline{forgets} a face.
			\item The scientist \underline{is working} on a new formular at the moment.
			\item The first train to London \underline{leaves} Broadstairs at 3:50\ in the morning.
			\item I \underline{ am not wearing} a jacket today, because it is too warm.
		\end{enumerate}
\end{document}
	
